Measurement and Probability in Fuzzy Quantum Theories

### 2017-01-22 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

\begin{definition}\cite{Hatcher2001,dryden2005} The unit sphere
in $\mathbb{R}^{d}$ is denoted by $S^{d-1}=\set{\ket{\psi}\in\mathbb{R}^{d}}{\ip{\psi}{\psi}=1}$,
while the unit sphere in $\mathbb{C}^{d}$ is denoted by $\mathbb{C}S^{d-1}=\set{\ket{\psi}\in\mathbb{C}^{d}}{\ip{\psi}{\psi}=1}$.
Since $\mathbb{C}$ is one-to-one correspondence to $\mathbb{R}^{2}$~\cite{GAMELIN2003},
$\mathbb{C}S^{d-1}$ has the same structure as $S^{2d-1}$. However,
different symbols emphasis that they are embedded in different spaces.\end{definition}

\begin{definition}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}
For any quantum probability measure~$\mu$ on the Hilbert space of
dimension 3, we can define a \emph{frame function}~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
by $f\left(\ket{\psi}\right)=\mu\left(\proj{\psi}\right)$. For a
quantum probability measure~$\mu_{\phi}^{B}$ induced by the Born
rule, its frame function is denoted by $f_{\phi}^{B}$.\end{definition}

\begin{lemma}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}
A frame function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
satisfies the following properties:
\begin{itemize}
\item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
$\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
\item $1=\sum_{i=1}^{3}f\left(\ket{\psi_{i}}\right)$ for any orthonormal
basis~$\left\{ \ket{\psi_{i}}\right\} _{i=1}^{3}$ of $\mathbb{C}^{3}$.
\end{itemize}
Conversely, if a function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
satisfies the above properties, $f$ must be a frame function.\end{lemma}

\begin{definition}For any quantum IVPM~$\bar{\mu}$ on the Hilbert
space of dimension 3, we can define an \emph{interval-valued frame
function}~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$ by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)$.
The left-end and the right-end of an interval-valued frame function
are $f^{l}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ and $f^{r}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
satisfying $\bar{f}\left(\ket{\psi}\right)=\left[f^{l}\left(\ket{\psi}\right),f^{r}\left(\ket{\psi}\right)\right]$,
respectively. Also, if $f$ is the frame function of $\mu$, $\bar{f}$
is the interval-valued frame function of $\bar{\mu}$, and $\mu$
is in the core of $\bar{\mu}$, then we say $f$ is in the core of
$\bar{f}$.\end{definition}

\begin{lemma}A interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the following properties:
\begin{itemize}
\item $\bar{f}\left(\lambda\ket{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
for any $\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
\item $1\in\sum_{i=1}^{3}\bar{f}\left(\ket{\psi_{i}}\right)$ for any orthonormal
basis~$\left\{ \ket{\psi_{i}}\right\} _{i=1}^{3}$ of $\mathbb{C}^{3}$.
\end{itemize}
\end{lemma}

Therefore, the set of 1-dimensional projectors mapping to impossible,
denoted by $\bar{\mu}^{-1}\left(\imposs\right)=\set{\ket{\psi}\in\mathbb{C}^{3}}{\bar{\mu}(\proj{\psi})=\imposs}$,
plays an important role to understand $\bar{\mu}$. There are 4 different
cases when analyzing $\bar{\mu}^{-1}\left(\imposs\right)$:
\begin{enumerate}
\item If another pair of states~$\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{\mu}^{-1}\left(\imposs\right)$
gives different state of cross product~$\ket{\psi_{0}'}\times\ket{\psi_{1}'}$,
then both $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
might induce $\bar{\mu}$, but neither $\mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$
nor $\mu_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ in the core
of $\bar{\mu}$ because $\mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$
is inconsistent with $\bar{\mu}(\proj{\psi_{0}'})=\bar{\mu}(\proj{\psi_{1}'})=\imposs$
and $\mu_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ is inconsistent
with $\bar{\mu}(\proj{\psi_{0}})=\bar{\mu}(\proj{\psi_{1}})=\imposs$.
Actually, $\bar{\mu}$ has an empty core. 
\item If $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
always represent the same state for all $\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{\mu}^{-1}\left(\imposs\right)$,
then $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is the only pure state
which might induce $\bar{\mu}$. In another word, if $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$
for some pure state~$\ket{\phi}$, then $\ket{\phi}$ and $\ket{\psi_{0}}\times\ket{\psi_{1}}$
represent the same state. 
\item $\bar{\mu}^{-1}\left(\imposs\right)$ may contain only one state~$\ket{\psi_{0}}$.
In this case, $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is undefined.
If $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$ for some
pure state~$\ket{\phi}$, $\ket{\phi}$ could be any state orthogonal
to $\ket{\psi_{0}}$.
\item $\bar{\mu}^{-1}\left(\imposs\right)=\emptyset$. If $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$
for some pure state~$\ket{\phi}$, we could say nothing about $\ket{\phi}$.
\end{enumerate}
In summary, if we have an idea of $\bar{\mu}^{-1}\left(\imposs\right)$,
we could have some idea of the pure states in core.

As we did in Fig.~\ref{fig:three-dimensional-4-value}, we could
plot the 1-dimensional projectors in a unit sphere~$S^{2}$~\cite{Hatcher2001,dryden2005}.
Since the state mapping to impossible always contained in a plane,
$\bar{\mu}^{-1}\left(\imposs\right)$ in the above case 2 - 4 does
not contain any area in $S^{2}$. In contrast, if $\bar{\mu}^{-1}\left(\imposs\right)$
contains some area in $S^{2}$, it must be the situation of case 1.
Furthermore, the larger the area, the more 1-dimensional projectors
which is inconsistent with any particular Born rule probability measure.
Therefore, the area of $\bar{\mu}^{-1}\left(\imposs\right)$ could
indicate how much $\bar{\mu}$ deviate from the Born rule probability
measures.

In order to simplify the discussion, let's set the center of $\bar{\mu}^{-1}\left(\imposs\right)$
as the north pole, and assume $\bar{\mu}$ maps every state whose
latitude is larger than $\theta_{0}$ to impossible. In order to simplify
the notation, let's give the following definition.

>>>>

\begin{definition}\cite{Hatcher2001,dryden2005}~The unit sphere
in $\mathbb{R}^{d}$ is denoted by $S^{d-1}=\set{\ket{\psi}\in\mathbb{R}^{d}}{\ip{\psi}{\psi}=1}$,
while the unit sphere in $\mathbb{C}^{d}$ is denoted by $\mathbb{C}S^{d-1}=\set{\ket{\psi}\in\mathbb{C}^{d}}{\ip{\psi}{\psi}=1}$.
Since $\mathbb{C}$ is one-to-one correspondence to $\mathbb{R}^{2}$~\cite{GAMELIN2003},
$\mathbb{C}S^{d-1}$ has the same structure as $S^{2d-1}$. However,
different symbols emphasis that they are embedded in different spaces.\end{definition}

\begin{definition}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}~For
any quantum probability measure~$\mu$ on the Hilbert space of dimension
3, we can define its \emph{frame function}~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
by $f\left(\ket{\psi}\right)=\mu\left(\proj{\psi}\right)$. For a
quantum probability measure~$\mu_{\phi}^{B}$ induced by the Born
rule, its frame function is denoted by $f_{\phi}^{B}$.\end{definition}

\begin{lemma}\cite{gleason1957,CookeKeaneMoran1985,peres1995quantum,RichmanBridges1999,Hamhalter2013}~A
frame function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ satisfies
the following properties:
\begin{itemize}
\item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
$\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=1}^{3}$,
we have $1=\sum_{i=1}^{3}f\left(\ket{\psi_{i}}\right)$.
\end{itemize}
Conversely, if a function~$f:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
satisfies the above properties, $f$ must be a frame function.\end{lemma}

\begin{definition}For any quantum IVPM~$\bar{\mu}$ on the Hilbert
space of dimension 3, we can define an \emph{interval-valued frame
function}~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$ by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}\left(\proj{\psi}\right)$.
The left-end and the right-end of an interval-valued frame function
are $f^{l}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$ and $f^{r}:\mathbb{C}S^{2}\rightarrow\left[0,1\right]$
satisfying $\bar{f}\left(\ket{\psi}\right)=\left[f^{l}\left(\ket{\psi}\right),f^{r}\left(\ket{\psi}\right)\right]$,
respectively. Also, if $f$ is the frame function of $\mu$, $\bar{f}$
is the interval-valued frame function of $\bar{\mu}$, and $\mu$
is in the core of $\bar{\mu}$, then we say $f$ is in the core of
$\bar{f}$, and denoted by $f\in\mathrm{core}\left(\bar{f}\right)$.\end{definition}

\begin{lemma}A interval-valued frame function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the following properties:
\begin{itemize}
\item $\bar{f}\left(\lambda\ket{\psi}\right)=\bar{f}\left(\ket{\psi}\right)$
for any $\ket{\psi}\in\mathbb{C}S^{2}$ and $\lambda\in\mathbb{C}S^{0}$.
\item For any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=1}^{3}$,
we have $1\in\sum_{i=1}^{3}\bar{f}\left(\ket{\psi_{i}}\right)$ and
$\left[1,1\right]-\bar{f}\left(\ket{\psi_{i}}\right)\subseteq\bar{f}\left(\ket{\psi_{j}}\right)+\bar{f}\left(\ket{\psi_{k}}\right)$,
where $i$, $j$, and $k$ are any permutations among $1$, $2$,
and $3$.
\end{itemize}
Conversely, if a function~$\bar{f}:\mathbb{C}S^{2}\rightarrow\mathscr{I}$
satisfies the above properties, $\bar{f}$ must be an interval-valued
frame function.\end{lemma}\footnote{\yutsung{{Verify the proof...}}}

Since interval-valued probability measures~$\bar{\mu}$ and interval-valued
frame functions~$\bar{f}$ are one-to-one correspondence, studying
1-dimensional projectors mapping to impossible by $\bar{\mu}$ is
the same as studying the points on $\mathbb{C}S^{2}$ mapping to impossible
by $\bar{f}$. These points, denoted by $\bar{f}^{-1}\left(\imposs\right)=\set{\ket{\psi}\in\mathbb{C}^{3}}{\bar{f}(\ket{\psi})=\imposs}$,
play an important role to understand $\bar{f}$. There are 4 different
cases when analyzing $\bar{f}^{-1}\left(\imposs\right)$:
\begin{enumerate}
\item If another pair of states~$\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{f}^{-1}\left(\imposs\right)$\footnote{\yutsung{{Check when }$\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}$ are
complex?}} gives different state of cross product~$\ket{\psi_{0}'}\times\ket{\psi_{1}'}$,
then both $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
might induce $\bar{f}$, but neither $f_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$
nor $f_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ in the core of
$\bar{f}$ because $f_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$ is
inconsistent with $\bar{f}(\proj{\psi_{0}'})=\bar{f}(\proj{\psi_{1}'})=\imposs$
and $f_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ is inconsistent
with $\bar{f}(\proj{\psi_{0}})=\bar{f}(\proj{\psi_{1}})=\imposs$.
Actually, $\bar{f}$ has an empty core. 
\item If $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
always represent the same state for all $\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{f}^{-1}\left(\imposs\right)$,
then $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is the only pure state
which might induce $\bar{f}$. In another word, if $f_{\phi}^{B}\in\mathrm{core}\left(\bar{f}\right)$
for some pure state~$\ket{\phi}$, then $\ket{\phi}$ and $\ket{\psi_{0}}\times\ket{\psi_{1}}$
represent the same state. 
\item $\bar{f}^{-1}\left(\imposs\right)$ may contain only one state~$\ket{\psi_{0}}$.
In this case, $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is undefined.
If $f_{\phi}^{B}\in\mathrm{core}\left(\bar{f}\right)$ for some pure
state~$\ket{\phi}$, $\ket{\phi}$ could be any state orthogonal
to $\ket{\psi_{0}}$.
\item $\bar{f}^{-1}\left(\imposs\right)=\emptyset$. If $f_{\phi}^{B}\in\mathrm{core}\left(\bar{f}\right)$
for some pure state~$\ket{\phi}$, we could say nothing about $\ket{\phi}$.
\end{enumerate}
In summary, if we have an idea of $\bar{f}^{-1}\left(\imposs\right)$,
we could have some idea of the pure states in core.

As we did in Fig.~\ref{fig:three-dimensional-4-value}, we could
plot the 1-dimensional projectors in a unit sphere~$S^{2}$~\cite{Hatcher2001,dryden2005}.
Since the state mapping to impossible always contained in a plane,
$\bar{f}^{-1}\left(\imposs\right)$ in the above case 2 - 4 does not
contain any area in $S^{2}$. In contrast, if $\bar{f}^{-1}\left(\imposs\right)$
contains some area in $S^{2}$, it must be the situation of case 1.
Furthermore, the larger the area, the more 1-dimensional projectors
which is inconsistent with any particular Born rule probability measure.
Therefore, the area of $\bar{f}^{-1}\left(\imposs\right)$ could indicate
how much $\bar{f}$ deviate from the Born rule probability measures.

In order to simplify the discussion, let's set the center of $\bar{f}^{-1}\left(\imposs\right)$
as the north pole, and assume $\bar{f}$ maps every state whose latitude
is larger than $\theta_{0}$ to impossible. In order to simplify the
notation, let's give the following definition.
